Temporal stability in human interaction networks: sector sizes, topological prominence and time activity

### 2015-08-21 paper.tex
incorporadas modificacoes da Deborah

\pacs{89.75.Fb,05.65.+b,89.65.-s}% PACS, the Physics and Astronomy
\keywords{complex networks, social network analysis, pattern recognition, statistics, anthropological physics}
\maketitle

@@

In this paper we analyze the evolution of human interaction networks, by considering interaction in email lists as their representative. Using a timeline of activity snapshots with a constant number of contiguous messages in email lists, we found a remarkable stability for several of the network properties. Because these properties were shared by networks from Twitter, Facebook and Participa.br, and are consistent with the literature, we advocate that some of the conclusions might be valid for more general classes of interaction networks. In particular, this allows us to discuss typologies in the context of such networks, in an attempt to bridge the gap between approaches based solely on data analysis (i.e. from a hard sciences perspective) and those relevant to the social sciences. This is important insofar as typologies are the canon of scientific literature for classification of human agents~\cite{typCanon}.

@@

A systematic study of the activity of participants belonging to the three distinct Erd\"os sectors indicated simple patterns for hubs and peripheral vertices, while the network structure was governed by the intermediary vertices. These properties were shared by all email lists and were time-independent, being consistent with the literature. Moreover, both the distribution of Erd\"os sectors and the contribution from the metrics to the PCA were found to apply to networks from Facebook, Twitter and Participa.br. We may therefore consider the classification of agents into Erd\"os sectors as a first step leading to a human typology which bridges exact sciences, with objective procedures for the classification, and human sciences, where there is a legacy in the observation of human types.

>>>>

\pacs{89.75.Fb,05.65.+b,89.65.-s}% PACS, the Physics and Astronomy
\keywords{complex networks, social network analysis, pattern recognition, statistics, anthropological physics, social psychology of big data}
\maketitle

@@

In this paper we analyze the evolution of human interaction networks, by considering interaction in email lists as their representative. Using a timeline of activity snapshots with a constant number of contiguous messages in email lists, we found a remarkable stability for several of the network properties. Because these properties were shared by networks from Twitter, Facebook and Participa.br, and are consistent with the complex networks literature, we advocate that some of the conclusions might be valid for more general classes of interaction networks. In particular, this allows us to discuss typologies in such contexts, in an attempt to bridge the gap between approaches based solely on data analysis (i.e. from a hard sciences perspective) and those relevant to the social sciences. This is important insofar as typologies are the canon of scientific literature for classification of human agents, with pragmatic standards~\cite{myers} and critical paradigms~\cite{adorno,typCanon}.

@@

A systematic study of the activity of participants belonging to the three distinct Erd\"os sectors indicated simple patterns for hubs and peripheral vertices, while the network structure was governed by the intermediary vertices. These properties were shared by all email lists and were time-independent, being consistent with the literature. Moreover, both the distribution of Erd\"os sectors and the contribution from the metrics to the PCA were found to apply to networks from Facebook, Twitter and Participa.br. We may therefore consider the classification of agents into Erd\"os sectors as a first step leading to a human typology which bridges exact sciences, with quantitative procedures for the classification, and human sciences, where there is a legacy in the observation of human types.
